---
title: "Psych 10 Project: Milestone 1"
author: 
---

NOTE: Submit this file as a .Rmd file on Canvas. 

The goals of Part 1 of your project are to:

* Identify your question and explain why you are asking it
* Identify, briefly describe, and read in your dataset to R
* Identify and descdribe the variables you will use to test your hypothesis.
* Identify challenges of this dataset and what data wrangling/cleaning you need to do. 
* Identify limitations of your project as a whole. 

# Environment set up 

__q1__ Set up your environment by loading the needed packages and saving the file path(s) to your data as values in your environment.
```{r}
#Libaries
#Load the packages you need here

#Files
#save the path to your datafile
# e.g., data_file <- "path"
```

# Project question

__q2__ What question will you answer in your project? 



__q3__ Motivation: Why is this question interesting and/or important to ask? Ground your explanation in fact. Provide at least one example of how answering this question may be useful in the "real" world. 


__q4__ Phrase your question in terms of a testable hypothesis. 



# The dataset

__q5__ What publically available dataset will you use for your project? Provide a brief description of this dataset (e.g., who collected it and when, what data does it contain, why was it collected, how were the data collected). 



__q6__ What file format is this dataset (e.g., .csv, .txt, .rds, .xlxs, data within R package)? How is your team sharing access to the dataset and your .Rmd files (e.g., a shared Box, Google Drive, or Dropbox folder)?



__q7__ Using one of the `readr`, `haven`, or `read_excel` functions to read in the data file and save it is a data frame in your R Studio Environment. If your dataset is in an R package, just save it as a data frame in your environment. 

```{r}

```

__q8__  Use the glimpse() function take a look at your dataset. How many observations are in your dataset and how many variables? 
```{r}

```

__q9__ Which variables will use to to test your hypothesis? Describe what they are. Include what types of variables they are (e.g., character, integer, etc.) and what their scales of measurement are. 


# Data challenges

_q10_ Is the raw dataset "tidy" (https://r4ds.had.co.nz/tidy-data.html)? Why or why not?


_q11_ What will you do to clean and wrangle your dataset to make it appropriate for analysis? For example, will you remove certain columns or rows? Do you need to rename or recode variables? 


# Project limitations

__q12__ Describe at least two limitations of your data that may make it challenging to draw particular conclusions or interpret your findings (e.g., consider who is in the sample and the design of the study)?


# Team member contributions

Please explain how each of your team members (by name) contributed to Part 1 of your project. 








