---
title: "Psych 10 Project: Milestone 2"
output: html_notebook:
   toc: true
   toc_float: true
---

NOTE: Submit this file as a .Rmd file on Canvas. 

This is Milestone 2 of your project. The goals of Milestone 2 of your project are to:

* Clean and wrangle your data and describe this process. 
* Visualize and summarize each of your variables and interpret what you see.  

# Environment set up 

__q1__ Set up your environment by loading the needed packages and saving the file path(s) to your data as values in your environment.
```{r}
#Libaries
#Load the packages you need here

#Files
#save the URL path that we provided to your data file 
# e.g., data_file <- "path"
```

# Read in your data

__q2__ Read in your data file using the appropriate function. 

```{r}

```


# Data cleaning and wrangling

__q3__ In Milestone 1, you described the necessary data cleaning and wrangling you would need to do to make it appropriate for analysis (q11). Perform this data cleaning below, as well as any additional cleaning/wrangling you need to do. For each data cleaning step, insert a separate chunk of code. For each step, explain why you are doing it in the whitespace below the chunk

```{r}
#data cleaning
```

DESCRIPTION

```{r}
#data cleaning
```

DESCRIPTION

# Data visualization and summary 

__q4__ Use `ggplot()` to create histograms (`geom_histogram` or `geom_col`) frequency polygons (`geom_freqpoly`) showing the distrbutions of each of the variables you are using to test your hypothesis. Only plot one variable per chunk of code. At the end, describe the distribution of each variable. 

```{r}

```

```{r}

```

DESCRIPTION


__q5__ Summarize each of the variables with the central tendency (and variance for ratio variables). If you have a group variable (e.g., country, school, age group), also summarize by group (hint: use the `group_by` function). Interpret your summary. 



